%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publication}

† Co-first author; * Corresponding author;

\pubitem
  {2026}
  {MetalloDock: Decoding Metalloprotein–Ligand Interactions via Physics-Aware Deep Learning for Metalloprotein Drug Discovery}
  {H. Zhang†, Xujun Zhang†, Qun Su†, Yangyang Zheng, Linlong Jiang, \textbf{\textcolor{awesome}{K. Zhu}}, et al. 
   \textbf{\textcolor{awesome}{J. Am. Chem. Soc. 2026, 148, 3, 3086–3101.}}}
  {6}

\pubitem
  {2025}
  {Enhanced Sampling in the Age of Machine Learning: Algorithms and Applications}
  {\textbf{\textcolor{awesome}{K. Zhu†}}, E. Trizio†, J. Zhang, R. Hu, L. Jiang, T. Hou*, L. Bonati*. 
   \textbf{\textcolor{awesome}{Chemical Reviews 126 (1), 671-713.}}}
  {5}

\pubitem
  {2025}
  {A Scalable and Quantum-Accurate Foundation Model for Biomolecular Force Field via Linearly Tensorized Quadrangle Attention}
  {Q. Su†, \textbf{\textcolor{awesome}{K. Zhu†}}, Q. Gou†, ..., J. Wang*, C. Hsieh*, T. Hou*.
   \textbf{\textcolor{awesome}{Nature Communications}}.}
  {4}

\pubitem
  {2025}
  {Self-Supervised Evolution Operator Learning for High-Dimensional Dynamical Systems}
  {G. Turri, L. Bonati, \textbf{\textcolor{awesome}{K. Zhu}}, M. Pontil, P. Novelli*
   \textbf{\textcolor{awesome}{ARXIV PREPRINT}} 2505.1867.}
  {3}
  
\pubitem
  {2025}
  {Revisiting Protein–Protein Docking: A Systematic Evaluation Framework.}
  {L. Jiang†, K. Zhang†, \textbf{\textcolor{awesome}{K. Zhu}}, Y. Wang, Y. Kang*, T. Hou*. 
   \textbf{\textcolor{awesome}{Journal of Chemical Information and Modeling}} 65(19), 10573–10587.}
  {2}
  
\pubitem
  {2025}
  {From Traditional Methods to Deep Learning Approaches: Advances in Protein–Protein Docking.}
  {L. Jiang, K. Zhang, \textbf{\textcolor{awesome}{K. Zhu}}, H. Zhang, C. Shen*, Tingjun Hou*. 
   \textbf{\textcolor{awesome}{Wiley Interdisciplinary Reviews: Computational Molecular Science}} 15(2), e70016.}
  {1}